Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-12-20 latex/ms.tex
add intro in Results section, #13

>>>>

We numerically evaluated the performance of ${\hat M}$ or ${\hat m}$ for the case in which variable reproductive potential among parents. Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$. {\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$). Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$) is summarized in {\bf Table S1} in {\bf Supporting Information}.

\subsection{Properties of ${\hat M}$}

%property of M_i (all are unbiased estimators (accuracy), M_3 shows the best performance (precision))

\subsection{Invasive sampling}

\subsection{Case of $N_1 \neq N_2$}
